---
title: "STAT545B_Assignment1"
output: github_document
author: "Jérôme Plumier"
date: "2023-11-01"
---

For this assignment, first we need to load some packages.

```{r}
library(tidyverse)
library (ggplot2)
library(datateachr) #contains dataset that shall be used to test the function
library(palmerpenguins) #contains dataset that shall be used to test the function
library(testthat) #package that allows evaluation and testing of our function
```


## Exercise 1: Make a Function (25 points)

I elected to create a function that creates a plot I have used for the mini data analysis project in STAT545A. This function permits the visualization of the number of NA values for each variable in a data frame.
I believe this function is valuable when encountering a new dataset.

```{r}
seeNA <- function(dataframe) {
  if(!(is.data.frame(dataframe))) {
    stop('The imput needs to be a data frame.')}
  if(sum(is.na(dataframe))==0) {
    stop('The dataframe has no NA values.')}
  if(sum(is.na(dataframe))==length(as.matrix(dataframe))){
    stop('The dataframe only has NA values.')}
  seeNA_dataframe <- dataframe%>% 
    summarise(across(everything(), ~ sum(is.na(.))))
  seeNA_dataframe <- as.data.frame(t(as.matrix(seeNA_dataframe))) 
  seeNA_dataframe$variable <- rownames(seeNA_dataframe)
  rownames(seeNA_dataframe) <- 1:nrow(seeNA_dataframe)
  colnames(seeNA_dataframe) <- c("NA_count", "Variable")
  ggplot(seeNA_dataframe, aes(y=Variable))+
  geom_bar(aes(weight=NA_count))+
  theme_bw() +
  xlab("Number of NA values")
}
```

## Exercise 2: Document your Function (20 points)

```{r}
seeNA <- function(dataframe) {
  if(!(is.data.frame(dataframe))) {
    stop('The imput needs to be a data frame.')}
  if(sum(is.na(dataframe))==0) {
    stop('The dataframe has no NA values.')}
  if(sum(is.na(dataframe))==length(as.matrix(dataframe))){
    stop('The dataframe only has NA values.')}
  seeNA_dataframe <- dataframe%>% 
    summarise(across(everything(), ~ sum(is.na(.))))
  seeNA_dataframe <- as.data.frame(t(as.matrix(seeNA_dataframe))) 
  seeNA_dataframe$variable <- rownames(seeNA_dataframe)
  rownames(seeNA_dataframe) <- 1:nrow(seeNA_dataframe)
  colnames(seeNA_dataframe) <- c("NA_count", "Variable")
  ggplot(seeNA_dataframe, aes(y=Variable))+
  geom_bar(aes(weight=NA_count))+
  theme_bw() +
  xlab("Number of NA values")
}

#' @title seeNA
#' @description Given a data frame, this function returns a bar graph with the variables of the dataset on the y-axis, and the number of NA values on the x-axis.
#' @param dataframe, a data frame object. Name that correspond to the parameter the most.
#' @return a bar graph that shows each variables and their number of NA values.

```


## Exercise 3: Include examples (15 points)

Given the `vancouver_trees` dataset that is part of the `datateachr` package as a parameter, this function returns a bar graph with the variables of the dataset on the y-axis, and the number of NA values on the x-axis.

```{r}
seeNA(vancouver_trees)
```

Given the `penguins` dataset that is part of the `palmerpenguins` package as a parameter, this function returns a bar graph with the variables of the dataset on the y-axis, and the number of NA values on the x-axis.

```{r}
seeNA(penguins)
```

Given the `steam_games` dataset that is part of the `datateachr` package as a parameter, this function returns a bar graph with the variables of the dataset on the y-axis, and the number of NA values on the x-axis.

```{r}
seeNA(steam_games)
```

## Exercise 4: Test the Function (25 points)

For this exercise, I tested my function using the `expect_error` function from the `testthat` package with three non-redundant inputs. They all passed:

```{r}
test_that('Not a data frame', {
x=2
expect_error(seeNA(x))
})
```

```{r}
test_that('Empty data frame', {
df1 <- data.frame()
expect_error(seeNA(df1))
})
```

```{r}
test_that('Only NA values in the data frame', {
df2 <- data.frame(
  X = c(NA, NA),
  y = c(NA, NA)) 
expect_error(seeNA(df2))
})
```